Approximation as Differentiation

### 2025-06-28 main/language.tex
Corrections.

To give the semantics for the language defined in \figrefTwo{syntax}{typing}, we fix a bicartesian closed
category $\Sem$ with finite products $(\times, 1)$, finite coproducts $(\coprod, 0)$ and exponentials
$\internalHom{X}{Y}$, with evaluation morphisms $\eval_{X,Y}$ and currying isomorphisms $\lambda_{X,Y,Z}$,
plus the following additional structure:
\begin{enumerate}
\item a strong monad $(\Lift, \eta, \mu)$ with strength $\mathsf{st}_{X,Y}: X \times \Lift(Y) \to \Lift(X
\times Y)$;
\item for each primitive type $\rho \in \PrimTy$, an object $\sem{\rho}_{\PrimTy}$;
\item for each primitive operation $\phi \in \PrimOp^\rho_{\rho_1,\ldots,\rho_n}$, a morphism $\sem{\phi}:
\sem{\rho_1} \times \ldots \times \sem{\rho_n} \to \sem{\rho}$
\item an endofunctor $\List: \Sem \to \Sem$, plus for any object $X$, morphisms $\nil: 1 \to \List(X)$ and
$\cons: X \times \List(X) \to \List(X)$, and for any objects $Y, Z$ and morphisms $f_\nil: Z \to Y$ and
$f_\cons: X \times Z \times Y \to Y$, a morphism $\fold(f_\nil,f_\cons): Z \times Y \times \List(X) \to Y$.
\end{enumerate}

>>>>

To give the semantics for the language defined in \figrefTwo{syntax}{typing}, we fix a bicartesian closed
category $\Sem$ with finite products $(\times, 1)$, finite coproducts $(\coprod, 0)$ and exponentials
$\internalHom{X}{Y}$, with evaluation morphisms $\eval_{X,Y}$ and currying isomorphisms $\lambda_{X,Y,Z}$,
plus the following additional structure:
\begin{enumerate}
\item a strong monad $(\Lift, \eta, \mu)$ with strength $\mathsf{st}_{X,Y}: X \times \Lift(Y) \to \Lift(X
\times Y)$;
\item for each primitive type $\rho \in \PrimTy$, an object $\sem{\rho}_{\PrimTy}$;
\item for each primitive operation $\phi \in \PrimOp^\rho_{\rho_1,\ldots,\rho_n}$, a morphism $\sem{\phi}:
\sem{\rho_1} \times \ldots \times \sem{\rho_n} \to \sem{\rho}$
\item an endofunctor $\List: \Sem \to \Sem$, plus for any object $X$, morphisms $\nil: 1 \to \List(X)$ and
$\cons: X \times \List(X) \to \List(X)$, and for any objects $Y, Z$ and morphisms $f_\nil: Z \to Y$ and
$f_\cons: Z \times X \times Y \to Y$, a morphism $\fold(f_\nil,f_\cons): Z \times \List(X) \to Y$.
\end{enumerate}
